\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

% Font options
% Disable typographic ligatures (e.g., fi, fl) for ATS readability
% and turn off font expansion to avoid issues with non-scalable fonts
\usepackage{microtype}
\microtypesetup{expansion=false}
\DisableLigatures{encoding = *, family = *}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Amiel Christian Estrada Mala-ay} \\ \vspace{1pt}
    Manila, Philippines \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +63 9273127609 ~ \href{mailto:amiel.malaay@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{amiel.malaay@gmail.com}} ~ 
    \href{https://amielchristian.github.io}{\raisebox{-0.2\height}\faGlobe\ \underline{amielchristian.github.io}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Santo Tomas}{Manila, Philippines}
      {BS Computer Science, specializing in Core Computer Science}{August 2021 -- June 2025}
      \resumeItemListStart
        \resumeItem{Latin Honors —\ \textit{Cum Laude}}
        \resumeItem{Dean's Lister, All Semesters}
        \resumeItem{GWA: 1.468 / 1.00}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  %-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Software Frameworks}{: React, Svelte, Electron, Flask, Django, Laravel} \\
    \textbf{Programming Languages and Environments}{: TypeScript, JavaScript, Java, Python, Kotlin, PHP, Node.js, Rust, SQL} \\
    \textbf{Databases}{: MySQL, PostgreSQL, SQLite, Redis} \\
    \textbf{Development Tools and Platforms}{: Git, GitHub, VS Code, Xcode, Android Studio, Docker} \\
    \textbf{AI/ML and Data Science}{: TensorFlow, Keras, Transformers, NumPy, Pandas, scikit-learn, SpaCy, NLTK} \\
    \textbf{Cloud Platforms}{: Google Cloud Platform, DigitalOcean, Firebase, Netlify, Vercel} \\
     \textbf{Languages}{: Filipino (native), English (native)}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Shoppable Business}{Manila, Philippines}
      {Software Developer Intern}{February 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Developed plugins and wrote documentation for Stackpress, a suite of open-source projects supported by the organization for future use in production applications.}
        \resumeItem{Aided in environment setup, debugging, and task allocation for other developer interns.}
        \resumeItem{Developed a test application using an in-house event-driven serverless framework and deployed it to Netlify.}
        \resumeItem{Kickstarted the development of a compiler for an in-house server-first template engine that generates native web components, using Rust.}
        \resumeItem{Developed UI components for code editing and display for an in-house UI library built with React, improving developer experience for internal tools.}
      \resumeItemListEnd

    \resumeSubheading
      {The Varsitarian}{Manila, Philippines}
      {Software Developer}{February 2025 -- April 2025}
      \resumeItemListStart
        \resumeItem{Rebuilt the scoreboard software from the ground up for the 45th edition of the publication's Pautakan 2025 competition using Electron, TypeScript, React, and Tailwind.}
        \resumeItem{Partnered with the event committee to develop a new design for the scoreboard and iterate over the shortcomings of the scoreboard used in the competition's previous edition.}
        \resumeItem{Assisted in the live presentation of the scoreboard during the competition, which garnered ~78,000 livestream viewers.}
      \resumeItemListEnd

    \resumeSubheading
      {8-Bit}{Manila, Philippines}
      {Full-Stack Developer}{August 2023 -- December 2024}
      \resumeItemListStart
        \resumeItem{Spearheaded the backend development for the UST College of Information and Computing Sciences' faculty attendance monitoring system (CICS-FAMS), built with Django, PostgreSQL, and Redis.}
        \resumeItem{Led client demos and feedback sessions and delivered continuous improvements to the system in line with Agile practices.}
        \resumeItem{Designed the database schema and REST API endpoints and took responsibility for deployment to an Ubuntu VPS and migration to on-premises hardware.}
        \resumeItem{Implemented Google authentication, automated emailing, and secure attendance logging using encrypted QR codes.}
        \resumeItem{Collaborated on UI design and frontend implementation for a diverse user base of student leaders, educators, and administrators.}
      \resumeItemListEnd

    \resumeSubheading
      {TomasinoWeb}{Manila, Philippines}
      {Backend Developer}{August 2023 -- June 2025}
      \resumeItemListStart
        \resumeItem{Built Ribbit, a simple microblogging platform utilizing Markdown formatting using Laravel and MySQL, in compliance with the requirements for recruitment into the organization.}
        \resumeItem{Performed schema redesign, restructured routing patterns, and implemented Recycle Bin functionality for the admin view for Draft143, a website for anonymous posts.}
        \resumeItem{Implemented Facebook feed integration for the Right Click website for university-level student council elections.}
        \resumeItem{Conducted fieldwork and data entry for Lamona, a food and drink directory catered to university students.}
      \resumeItemListEnd

    \resumeSubheading
      {The Varsitarian}{Manila, Philippines}
      {Software Developer}{February 2024 -- April 2024}
      \resumeItemListStart
        \resumeItem{Developed the scoreboard software used in the 44th edition of the publication's Pautakan 2024 competition using the Electron JavaScript framework, collaborating with the event committee and Creatives department on UI.}
        \resumeItem{Supported the live presentation of the scoreboard during the competition, which reached ~186,000 livestream viewers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP & ACTIVITIES-----------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Thesis}{Manila, Philippines}
      {}{January 2024 -- January 2025}
      \resumeItemListStart
        \resumeItem{Proposed T2Distill-GradCAM, a novel framework for diabetic retinopathy diagnosis based on the Vision Transformer (ViT) architecture, leveraging knowledge distillation, class activation mapping (CAM), convolutional neural networks (CNN), and convolutional autoencoders (CAE).}
        \resumeItem{Formulated and implemented a cross-architecture two-teacher knowledge distillation framework that extracts CAM images from a CNN, passes them to a CAE, and aligns the CAE's feature maps with those of the ViT using spatial alignment in TensorFlow and Keras, achieving 78.74\% test accuracy (baseline: 77.24\%).}
        \resumeItem{Strongly accepted for publication and presentation at the 25th International Conference on Computing and Artificial Intelligence in Kyoto, Japan, and awarded first place in the University of Santo Tomas Core Computer Science Research Colloquium.}
      \resumeItemListEnd

    \resumeSubheading
      {UST Thomasian Gaming Society}{Manila, Philippines}
      {Evaluations Staff}{August 2024 -- June 2025}
      \resumeItemListStart
        \resumeItem{Founding member responsible for composing reports synthesizing attendee feedback from organizational events.}
        \resumeItem{Analyzed evaluation forms using qualitative and quantitative methods to inform improvements for future event planning.}
      \resumeItemListEnd

    \resumeSubheading
      {UST Computer Science Society}{Manila, Philippines}
      {Academics Committee Staff}{August 2023 -- June 2024}
      \resumeItemListStart
        \resumeItem{Collaborated in creating reviewers and organizing academic events, including the 2024 Computer Science Research Colloquium, to support examination readiness and student engagement.}
      \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Projects}{Manila, Philippines}
      {}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented BINI, an AI prompt safety classifier for Tagalog-language prompts with a test accuracy of 97.12\%, successful at preventing all but 0.44\% of adversarial prompts when tested on the LLaMa-70B model, using DistilmBERT, mBERT, and XLM-RoBERTa.}
        \resumeItem{Fine-tuned pretrained neural network models such as VGGNet16 and MobileNet for detecting brain tumors in MRI images, achieving a validation accuracy of 99.01\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Development Projects}{Manila, Philippines}
      {}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented an interpreter for a toy language called Ror, using a deterministic finite automaton-based tokenizer, lexical analyzer, and syntax analyzer, all hand-crafted using Java.}
        \resumeItem{Built a high-performing e-commerce application with a seamless, user-friendly interface for local farmers and coffee shops using Django.}
        \resumeItem{Developed a Markdown-based wiki and a bidding website using Django as part of the Harvard CS50 Web program.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Awards and Certifications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Best Thesis} $|$ \emph{University of Santo Tomas Computer Science Department}}{April 2025}
    \resumeProjectHeading
      {\textbf{Introduction to Machine Learning on AWS} $|$ \emph{Amazon Web Services}}{August 2024}
    \resumeProjectHeading
      {\textbf{JavaScript Algorithms and Data Structures} $|$ \emph{freeCodeCamp}}{July 2023}
  \resumeSubHeadingListEnd

\end{document}